Predicting Spotify Audio Features from Last.fm Tags

### 2023-05-12 paper/main.tex
add comments
add missing results in table
improving input formatting section

\title[Predicting Audio Features with Last.fm Tags]{Predicting Audio Features with Last.fm Tags}

@@

Both types of values have been used as input values mostly for classification tasks, such as music genre recognition,
where, given Spotify features or Last.fm tasks, the model estimates the music genres of a particular track.
However, these values have not been used as target values by previous research, to the best of our knowledge.
In particular, the focus of this article is on predicting Spotify audio features, given a set of Last.fm tags.

@@

Additionally, predicted audio features could be used in recommendation systems to provide users with explainable recommendations.
Music recommendations,are not always easy to interpret from the perspective of the listener.
Users often get recommendations without meaningful explanations or justifications.
Therefore, by using predicted Spotify features as basis for recommendation, we can explain users why the algorithm suggests a particular track.
This process could be part of an explainable recommendation pipeline, where users enter a set of tags,
and they receive the predicted audio features, the closest tracks to those features, and the distance values between each track and the predicted features.

@@

In recent years, researchers have studied the use of Last.fm tags in classification and regression tasks.
Several studies have used Last.fm to predict music sentiment or mood.

In the last decade, Last.fm tags have been a popular source of metadata for MIR tasks.
Last.fm tags can contain subjective information the genre, mood, and style of music,
and might be use to characterize certain features of a music piece.

Last.fm tags can be useful when the audio signal available,
for example, due to copyright limitations.

A number of studies have explored the use of Last.fm tags in MIR,
and have shown promising results in predicting various audio features.
% For example, tags such as "acoustic", "live", and "instrumental" have been
% shown to be good predictors of the energy and danceability of a track.
% Similarly, tags such as "happy," "sad," and "angry" have been used
% to predict the valence and arousal of a track.

Researchers have used Last.fm tags.
For example, Laurier et al. analyzed how Last.fm tags categorize mood.
In their study, they created a semantic mood space based on Last.fm tags \cite{laurier2009music}.

For example, {\c{C}}ano and Morisio discuss the process they follow to create a dataset of music
lyrics annotated with Last.fm.
In the creation process, they conclude that Last.fm tags are mostly related to music genre
and positive moods \cite{ccano2017music}.
In a similar direction, Bod{\'o} and Szil{\'a}gyi generated a dataset for lyrics genre classification
by combining the Last.fm with MusicBrainz data \cite{bodo2018connecting}.
MusicBrainz \footnotemark[1] is an online database of music editorial metadata.
\footnote[1]{https://musicbrainz.org/}

The Last.fm data has been the most widely used Last.fm dataset\footnotemark[2] in research.
This dataset is a complementary dataset of the Million Song Dataset (MSD) \cite{Bertin-Mahieux2011}.

@@

Spotify, one of the leaders in the music streaming industry...

Additionally, the Spotify audio features have been used in multiple studies.
Historically, these features were also called \emph{Echo Nest audio features}.
Spotify adquired Echo Nest in 2014 and made the audio features available via the Spotify  API
\footnote[3]{https://en.wikipedia.org/wiki/The\_Echo\_Nest}.
Echonest was an online platform that was later acquired by Spotify.
% https://en.wikipedia.org/wiki/The_Echo_Nest

Wang and Horv{\'a}t use audio features to study differences between male and female artists \cite{wang2019gender}

In general, these studies confirm the possibility of extracting knowledge from Last.fm tags.
To the best of our knowledge, no studies have addressed the problem of audio features regression, based solely on Last.fm tags.

@@

P4kxspotify is a publicly available dataset that combines music review texts with Spotify audio features.
The dataset creators argue that, although the terms of service prohibits scraping, their work is ethical \cite{pinter2020p4kxspotify}.

In general, Spotify audio features have been used as predictive variables.
We, to the best of our knowledge, are unaware of students that uses these features as target variables.

While Spotify provides a description of the high-level audio features, how they compute or estimate these values is not publicly available.
Panda and Redinho explore the use of Spotify high-level features applied to Music Emotion Recognition (MER) \cite{panda2021does}.
In particular, they identify that the energy, valence, and acousticness values, provided by the Spotify API,
are highly relevant for emotion classification.
They also achieve better performance on MER models by using their own top-100 features, and they determine that,
although these three Spotify features are relevant in terms of characterizing emotion, more features are needed for MER.

@@

This work is scoped within our single-user research area \cite{ramirez2022user}.
In this area, we explore the development of music recommender systems that
characterize the music preferences and listening context only for a single user.
By training our system with single-user data, we also explore the following question: Is it possible to train
recommender systems, and in particular, user-centric systems, by using a single-user dataset?

The user data for this work has been extracted from the
listening history of the corresponding author user in Last.fm
\footnote[4]{https://www.last.fm/user/jimmydj2000}.

Similar to other intelligent systems, recommender systems
must be trained, by using user preference data, to produce
suitable recommendations. For this study,
we leverage the knowledge discovery potential
of large historical listening logs, gathered from Last.fm.

@@

Last.fm uses the term \emph{scrobble} to refer to a single track playback,
at a particular moment.
We queried the Last.fm API to download the user{'}s scrobble logs, reported from 2007 to 2022.
For each scrobble, we have gathered the following information:

\begin{itemize}
\item Playback timestamp
\item Track name
\item Artist name
\item Track tags. If the track does not have any tags assigned,
then artist tags have been used
\end{itemize}

For each tag-track mapping, Last.fm includes
a \emph{count} value, which indicates the popularity of the given tag for the track.
Last.fm normalizes this value in the 0-100 range, so the most popular tag for a track can have a
count value of 100.
For example, if \emph{piano} is the most popular tag for a track,
then the track might be probably
associated to the following tuple \verb|(piano, 100)|.

Users normally listen to their favorite tracks several times,
so the amount of unique tracks listened is much smaller
than the number of track plays. In this case, the amount of
individual tracks listened is about 20,000, and the number of scrobblings is, approximately, 90,000.

@@

The features provided by the Spotify API are listed in
Table \ref{table:spotify-features}.
The reader can find further details about each feature in the Spotify API documentation
\footnote[5]{
      \url{https://developer.spotify.com/documentation/web-api/reference/\#/operations/get-audio-features}
}.

@@

The Spotify API failed to provide audio features for a portion of the tracks.
These tracks were filtered out from our experiments.
After filtering tracks that miss Last.fm tags or Spotify audio features,
our dataset contains 14,009 samples.

Considering that the data was gathered from a single user,
we explored the data to verify that the distribution of the Spotify audio features
was comparable to other Spotify datasets.
In particular, we verified that the distribution of the features,
described in Table \ref{table:audio-features-stats} and Figure \ref{fig:audio-features-distribution},
was comparable to the distribution of the \emph{Spotify Audio Features} Kaggle dataset.
This dataset contains more tha 116,000 unique tracks, and includes audio features for each track.
Our dataset present similar $\mu$ and $\sigma$ values as the Spotify Audio Features Kaggle dataset,
as illustrated in Table \ref{table:audio-features-stats-kaggle} and Figure \ref{fig:audio-features-distribution-kaggle}.
\footnote[6]{https://www.kaggle.com/datasets/tomigelo/spotify-audio-features}.

@@

Not every track of the approximately unique tracks 20,000 of the Last.fm user{'} listening history
included Last.fm tags and Spotify audio features.
Tracks without Last.fm tags or without Spotify audio features were filtered out.
As a result, of the originally 20,000 tracks included in the listening history,
our dataset final size resulted in 14,009 samples.

@@

We trained commonly used machine learning models to predict an audio feature, given the set of tags for a particular track.

@@

The number of columns is limited to the top-K tags.
Counting the total amount of Last.fm tags in the user collection resulted, initially, in more than five million tags.
We quickly confirmed that building a tabular data set, in which every row contains millions of columns (Last.fm tags)
was doable, but presented scalability problems.
Therefore, we reduced the number of tags by picking a subset of the most relevant tags.

The reduction algorithm is simple: calculate a weighted sum of all the tags appearances and pick the top 1000.
The sum is weighted be- cause we use the count attribute.
This attribute is present in every Last.fm track-tag association and provides a measure of the strength of a particular tag in a specific track.
Note that this reduction is an initial approach, which, similar to other phases, can be extended or improved in the future. For this particular case, dimensionality reduction algorithms, such as PCA, are good candidates for forthcoming iterations of this work.

The input data passed is formatted in tabular format, as follows:

\begin{itemize}
      \item Given that $Tags_{k}$ is the set of most $k$ frequent Last.fm tags in the user listening history
            and, where each $tag \in Tags_{k}$.
      \item Given that $Audio$ is the set of Spotify audio features, where each $feat \in Audio$.
      \item For each $track$:
      \begin{itemize}
            \item $X_{track},_{tag}$ is the strengh of $tag$ for $track$. This value is in the $0-100$ range.
            \item $y_{track},_{feature}$ is the value of the audio feature $y$ for $track$.
      \end{itemize}
\end{itemize}

@@

\begin{itemize}
      \item By including tag popularity: `rock 2, pop 1`.
      \item By repeating tags based on popularity: `rock rock, pop`.
      \item By ordering by popularity: `rock, pop`.
\end{itemize}

In this particular case, the $X$ values of the tabular input data are tokens.
These tokens are obtained from passing the a string of concatenated Last.fm tags through a tokenizer.
The formal definition of this data format is as follows:

\begin{itemize}
      \item Given that $X_l$ is the token vocabulary, where $l$ is the maximum vocabulary length.
      \item Given that $Audio$ is the set of Spotify audio features, where each $feat \in Audio$.
      \item For each $track$:
      \begin{itemize}
            \item $X_{track},_{n}$ is token found at position $n$, after tokenizing the tags string.
            \item $y_{track},_{feature}$ is the value of the audio feature $y$ for $track$.
      \end{itemize}
\end{itemize}

@@

\subsection{Text}

When using transformer models, the input data is a string.
We must represent the Last.fm tags, which are initially in the $(tag name, tag popularity)$ form, to a a string.

@@

\begin{table}[h]
      \begin{center}
      \begin{minipage}{\textwidth}
      \caption{Text data format for tokens in XGBoost and Bayesian regressors}\label{text_format}%
      \begin{tabular}{@{}lllll@{}}
      \toprule
      Track                         & $X$                                   & $y_{energy}$ & $y_{valence}$ & $y_{\dots}$ \\
      \midrule
      Massive Attack - Blue Lines   & "hip hop, chill, bristol, \dots"      & 0.496        & 0.947         & \dots  \\
      The Beta Band - Squares       & "alternative rock, folk, \dots"       & 0.446        & 0.507         & \dots \\
      \dots                         & \dots                                 & \dots        & \dots         & \dots  \\
      \botrule
      \end{tabular}
      \end{minipage}
      \end{center}
\end{table}

@@

\begin{table}[h]
      \begin{center}
      \begin{minipage}{174pt}
      \caption{Training parameters for XGBoost regressor}\label{table_xgboost_training_params}%
      \begin{tabular}{@{}llll@{}}
      \toprule
      Parameter               & Value \\
      \midrule
      objective               & reg:squarederror  \\
      base score              & 0.5 \\
      booster                 & gbtree  \\
      colsample bylevel       & 1 \\
      colsample bynode        & 1 \\
      colsample bytree        & 1 \\
      gamma\footnotemark[1]   & 0 \\
      learning rate           & 0.300000012 \\
      max delta step          & 0 \\
      max depth               & 6 \\
      min child weight        & 1 \\
      estimators              & 200  \\
      n jobs                  & 12  \\
      num parallel tree       & 1 \\
      predictor               & auto  \\
      random state            & 0 \\
      reg alpha               & 0 \\
      reg lambda              & 1 \\
      scale pos weight        & 1 \\
      subsample               & 2 \\
      tree method             & auto  \\
      \botrule
      \end{tabular}
      \footnotetext[1]{Minimum loss reduction required to make a further partition on a leaf node of the tree.}
      \end{minipage}
      \end{center}
\end{table}

@@

@@

      GPT       & Duplicated\footnotemark[5]          & 0.157            & ...             & ...            & ...             & ...            \\
      GPT       & Ordered\footnotemark[6]             & 0.149            & ...             & ...            & ...             & ...            \\
      GPT       & Tags,Counts\footnotemark[7]         & \textbf{0.145}   & ...             & ...            & ...             & ...            \\

>>>>

\title[Predicting Spotify Audio Features from Last.fm Tags]{Predicting Spotify Audio Features from Last.fm Tags}

@@

Both types of values have been used as input data mostly for classification tasks, such as music genre recognition,
where, given Spotify features or Last.fm tasks, the model estimates the music genres of a particular track.
Previous studies, however, have not used these values as target outputs, to the best of our knowledge.
In particular, the focus of this article is on predicting Spotify audio features, given a set of Last.fm tags.

@@

Additionally, predicted audio features could be used in recommendation systems to provide users with explainable recommendations.
Music recommendations are tipically dificult to interpret from the perspective of the listener.
Users often get recommendations without meaningful explanations or justifications.
Therefore, by using predicted Spotify features as basis for recommendation, we can explain users why the algorithm suggests a particular track.
This process could be part of an explainable recommendation pipeline, where users enter a set of tags,
and they receive the predicted audio features, the closest tracks to those features, and the distance values between each track and the predicted features.

@@

\subsubsection{Last.fm Tags}

In the last decade, researchers have studied the use of Last.fm tags in classification and regression tasks.
Last.fm tags have been a popular source of metadata for MIR tasks,
because they potentionally contain subjective information related to the genre, mood, and style of music,
and might be used to characterize certain features of a music piece.
Several studies have used Last.fm to predict music sentiment or mood, and to predict audio features.

Additionally, Last.fm tags constitute a useful source of input knownledge when the audio signal is not available,
for example, due to copyright limitations.

% == Excerpt taken from one of our references vvvvvvv
% For example, tags such as "acoustic", "live", and "instrumental" have been
% shown to be good predictors of the energy and danceability of a track.
% Similarly, tags such as "happy," "sad," and "angry" have been used
% to predict the valence and arousal of a track.

For example, Laurier et al. analyze how Last.fm tags categorize mood.
In their study, they created a semantic mood space based on Last.fm tags \cite{laurier2009music}.

{\c{C}}ano and Morisio discuss how they create a dataset of music
lyrics annotated with Last.fm tags.
In the creation process, they conclude that Last.fm tags are mostly related to music genre
and positive moods \cite{ccano2017music}.

In a similar direction, Bod{\'o} and Szil{\'a}gyi generate a dataset for lyrics genre classification
by combining the Last.fm with MusicBrainz data \cite{bodo2018connecting}.
MusicBrainz is an online database of music editorial metadata\footnote[1]{https://musicbrainz.org/}.

So far, The \emph{Last.fm dataset} has been the most widely used Last.fm dataset\footnotemark[2] in research.
This dataset is a complementary dataset of the Million Song Dataset (MSD) \cite{Bertin-Mahieux2011}.

@@

In general, these studies confirm the possibility of extracting knowledge from Last.fm tags.

\subsubsection{Spotify Audio Features}

% Spotify, one of the leaders in the music streaming industry...

The Spotify audio features have been used in multiple studies.
Historically, these features were called the \emph{Echo Nest audio features}.
\emph{The Echo Nest} was an online music intelligence platform that provided users and clients with music analysis services.
Among these services, the Echo Nest offered a database and an API to retrieve audio features for each of the tracks in the database \footnote[3]{https://en.wikipedia.org/wiki/The\_Echo\_Nest}.
Spotify acquired the Echo Nest in 2014.
As a result, the Echo Nest API was shut down and Spotify made these audio features available via the Spotify API.

Nowadays, published research is available under the two terms.
Whereas the most recent studies refer to these audio features as the Spotify audio features,
earlier studies use the Echo Nest denomination.

Regardless of the term used, the features remain the same.
These features are a set of high-level descriptors, such as energy and danceability,
which are related to the audio but also to the listeners perception.

While Spotify provides a description of the audio features, how they compute or estimate these values is not publicly available.

Wang and Horv{\'a}t use audio features to study differences between male and female artists \cite{wang2019gender}.

@@

Panda and Redinho explore the use of Spotify high-level features applied to Music Emotion Recognition (MER) \cite{panda2021does}.
In particular, they identify that the energy, valence, and acousticness values, provided by the Spotify API,
are highly relevant for emotion classification.
They also achieve better performance on MER models by using their own top-100 features, and they determine that,
although these three Spotify features are relevant in terms of characterizing emotion, more features are needed for MER.

Publicly available datasets of Spotify audio features can be found online,
as a result of open-source and research communities collecting data from the Spotify API and publishing the results.
It is unclear, however, whether these published datasets violate the Spotify API terms of service.

For example, \emph{P4kxspotify} is a publicly available dataset that combines music review texts with Spotify audio features.
The dataset creators argue that, although the terms of service prohibits scraping, their work is ethical \cite{pinter2020p4kxspotify}.

Another example is the \emph{Spotify Audio Features} Kaggle dataset\footnote[4]{https://www.kaggle.com/datasets/tomigelo/spotify-audio-features}.
This dataset contains more than 116,000 unique tracks, and includes audio features for each track.

In general, Spotify audio features have been used as predictive input variables.
We, to the best of our knowledge, are unaware of studies that use these features as target variables,
or studies that have addressed the problem of audio features regression, based solely on Last.fm tags.

@@

This work is scoped within our single-user research line \cite{ramirez2022user}.
In this area, we explore the development of music recommender systems that
characterize the music preferences and listening context only for a single user.
By training our system with single-user data, we also raise the following question: Is it possible to train
recommender systems, and in particular, user-centric systems, by using a single-user dataset?

The user data for this work has been extracted from the
listening history of the corresponding author user in Last.fm\footnote[5]{https://www.last.fm/user/jimmydj2000}.

Similar to other intelligent systems, recommender systems
must be trained, by using user preference data, to produce
suitable recommendations. For this study,
we leverage the knowledge discovery potential
of large historical listening logs, gathered for the mentioned user from Last.fm.

@@

Last.fm uses the term \emph{scrobble} to refer to the action of playing a track at a specific moment in time.
Initially, Last.fm monitored user listening activity with a desktop application called \emph{Scrobbler}.
Users used to install this application on their computers to monitor their activity on players such as Winamp or iTunes.
With the advent of music streaming services, the possibilities for users to scrobble their music habits expanded.
Integrations where developed to integrate the scrobbler into popular platforms,
such as Spotify, YouTube, or SoundCloud.
Mobile versions of the Scrobbler were developed for Android and iOS devices, and also open source initiatives flourished\footnote[6]{https://github.com/elamperti/OpenWebScrobbler}.

For us, the first step to construct the dataset was to download the user listening activity.
We queried the Last.fm API to download the user{'}s scrobbling logs, reported from 2007 to 2022.
For each scrobble, we have gathered the following information:

\begin{itemize}
\item Playback timestamp.
\item Track name.
\item Artist name.
\item Track tags. If the track does not have any tags assigned,
then artist tags were used.
\end{itemize}

Last.fm maps each track (and artist) to a list of community-contributed tags.
For each track-tag mapping, Last.fm includes
a \emph{count} value, which indicates the popularity of the given tag for the track.
Last.fm normalizes this value in the 0-100 range, so the most popular tag for a track can have a
count value of 100.
For example, if \emph{jazz club} is the most popular tag for a track,
then the track might be probably
associated to the following tuple \verb|(jazz club, 100)|.

Users tipically listen to their favorite tracks several times,
so the amount of unique tracks played is much smaller
than the number of track plays. In this case, the amount of
individual tracks listened is about 20,000 and the number of scrobblings is, approximately, 90,000.
Therefore, the user has listened to each song, approximately, 4.5 times on average.

@@

The features provided by the Spotify API are listed in
Table \ref{table:spotify-features}.
The reader can find further details about each feature in the Spotify API documentation\footnote[5]{
      \url{https://developer.spotify.com/documentation/web-api/reference/\#/operations/get-audio-features}
}.

@@

After gathering the data, we identified that the Spotify API had failed to provide audio features for a portion of the tracks.
Similarly, Last.fm also returned no tags for another subset of the tracks.
To prevent problems with missing values, we decided to filter out these tracks from the dataset, and therefore, from our experiments.
After filtering tracks that were missing Last.fm tags or Spotify audio features,
the dataset resulted in 14,009 samples.
Compared to the original 20,000 unique tracks included in the listening history, approximately 6,000 songs were missing either Spotify or Last.fm data.

\subsection{Dataset Comparison}

Considering that the data was gathered from a single user,
we explored the data to verify that the distribution of the Spotify audio features
was comparable to larger, and possibly more balanced, Spotify datasets.
In particular, we verified that the distribution of the features,
described in Table \ref{table:audio-features-stats} and Figure \ref{fig:audio-features-distribution},
was comparable to the distribution of the \emph{Spotify Audio Features} Kaggle dataset.
Our dataset presents similar $\mu$ and $\sigma$ values to the Spotify Audio Features Kaggle dataset,
as illustrated in Table \ref{table:audio-features-stats-kaggle}
and Figure \ref{fig:audio-features-distribution-kaggle}.

@@

@@

We trained commonly used machine learning models to predict Spotify audio features, given the set of Last.fm tags for a particular track.

@@

Counting the total amount of Last.fm tags in the user collection resulted, initially, in more than five million tags.
We quickly confirmed that building a tabular data set, in which every row contains millions of columns (Last.fm tags)
was doable, but presented scalability problems.
Therefore, we reduced the number of tags by picking a subset of the most relevant tags.

The reduction algorithm uses a basic data aggregation algorightm: group the data by tag, aggregate by summing the \emph{count} values for each tag,
order by the aggregated count, and finally select the top-$K$ items of the ranking.

We generated three versions of the dataset, with different values of $K$: 100, 1,000 and 10,000.

We consider this reduction approach an initial approach.
For this particular aspect, dimensionality reduction algorithms, such as PCA, are good candidates for future work.

After selecting the top-$K$ tags, the input data passed was formatted in tabular format, as follows:

\begin{itemize}
      \item Given that $Tags_{K}$ is the set of most $K$ frequent Last.fm tags in the user listening history
            and, where each $tag \in Tags_{K}$.
      \item Given that $Audio$ is the set of Spotify audio features, where each $feat \in Audio$.
      \item For each $track$:
      \begin{itemize}
            \item $X_{track},_{tag}$ is the strengh of $tag$ for $track$. This value is in the $0-100$ range.
            \item $y_{track},_{feature}$ is the value of the audio feature $y$ for $track$.
      \end{itemize}
\end{itemize}

@@

\begin{itemize}
      \item Ordering by count: \verb|"rock, pop"|.
      \item Including tag count: \verb|"rock 2, pop 1"|.
      \item Duplicating each tag $count$ times: \verb|"rock rock, pop"|.
\end{itemize}

In this particular case, the $X$ values of the tabular input data are tokens.
These tokens are obtained from passing the string of concatenated Last.fm tags through the GPT-2 tokenizer,
as the following procedure explains:

\begin{itemize}
      \item Given that $X_L$ is the token vocabulary, where $L$ is the maximum vocabulary length.
      \item Given that $Audio$ is the set of Spotify audio features, where each $feat \in Audio$.
      \item For each $track$:
      \begin{itemize}
            \item $X_{track},_{n}$ is token found at position $n$, after tokenizing the tags string.
            \item $y_{track},_{feature}$ is the value of the audio feature $y$ for $track$.
      \end{itemize}
\end{itemize}

@@

Similarly to the tags tabular format, we also defined fixed values for the number of columns: 10, 1,000, and 10,000.

The two tabular formats, with tags and tokens, were tested on the Naive Bayes and the Boosted tree regressors.

\subsection{Text Strings}

When using transformer models, the input data is a string.
We must represent the Last.fm tags, which are defined as $(tag, count)$ tuples, as strings.
To this end, we applied the same three transformations used in the tabular tokens formats,
concatenate the tags by ordering by count, by including the tag count, and by duplicating the tags.

@@

\begin{table}[h]
      \begin{center}
      \begin{minipage}{\textwidth}
      \caption{Text data format for GPT-transformer. In this particular case, the tags have been concatenated by ordering by tag count}\label{text_format}%
      \begin{tabular}{@{}lllll@{}}
      \toprule
      Track                         & $X$                                   & $y_{energy}$ & $y_{valence}$ & $y_{\dots}$ \\
      \midrule
      Massive Attack - Blue Lines   & "hip hop, chill, bristol, \dots"      & 0.496        & 0.947         & \dots  \\
      The Beta Band - Squares       & "alternative rock, folk, \dots"       & 0.446        & 0.507         & \dots \\
      \dots                         & \dots                                 & \dots        & \dots         & \dots  \\
      \botrule
      \end{tabular}
      \end{minipage}
      \end{center}
\end{table}

@@

\begin{table}[h!]
      \begin{center}
      \begin{minipage}{174pt}
      \caption{Training parameters for XGBoost regressor}\label{table_xgboost_training_params}%
      \begin{tabular}{@{}llll@{}}
      \toprule
      Parameter               & Value \\
      \midrule
      objective               & reg:squarederror  \\
      base score              & 0.5 \\
      booster                 & gbtree  \\
      colsample bylevel       & 1 \\
      colsample bynode        & 1 \\
      colsample bytree        & 1 \\
      gamma\footnotemark[1]   & 0 \\
      learning rate           & 0.300000012 \\
      max delta step          & 0 \\
      max depth               & 6 \\
      min child weight        & 1 \\
      estimators              & 200  \\
      n jobs                  & 12  \\
      num parallel tree       & 1 \\
      predictor               & auto  \\
      random state            & 0 \\
      reg alpha               & 0 \\
      reg lambda              & 1 \\
      scale pos weight        & 1 \\
      subsample               & 2 \\
      tree method             & auto  \\
      \botrule
      \end{tabular}
      \footnotetext[1]{Minimum loss reduction required to make a further partition on a leaf node of the tree.}
      \end{minipage}
      \end{center}
\end{table}

@@

% INFO - Training Set: (8654, 14)
% INFO - Validation Set: (2164, 14)
% INFO - Test Set: (2705, 14)

% TRAINING STATS
% Num examples = 8654
% Num Epochs = 10
% Instantaneous batch size per device = 10
% Total train batch size (w. parallel, distributed & accumulation) = 10
% Gradient Accumulation steps = 1
% Total optimization steps = 8660
% Number of trainable parameters = 124441344

@@

      GPT       & Duplicated\footnotemark[5]          & 0.157            & 0.244           & 0.193          & 0.245           & 0.322          \\
      GPT       & Ordered\footnotemark[6]             & 0.149            & \textbf{0.237}  & 0.188          & 0.235           & \textbf{0.297}          \\
      GPT       & Tags,Counts\footnotemark[7]         & \textbf{0.145}   & \textbf{0.237}  & \textbf{0.187} & \textbf{0.233}  & 0.301          \\
